### 2015-07-07 paper.tex
add the abstract and a litter modify

	\fancyhead[c]{\small Chinese Physics C~~~Vol. XX, No. X (201X)
	XXXXXX} \fancyfoot[C]{\small 010201-\thepage}
	\footnotetext[0]{Received XX XXXX 20XX}

	\title{The event rate estimation for JUNO experiment \thanks{Supported by National Natural Science Foundation of China (NSFC) under Contracts Nos. xxx, xxx; the Chinese Academy of Sciences (CAS) Large-Scale Scientific Facility Program; Joint Large-Scale Scientific Facility Funds of the NSFC and CAS under Contracts Nos.  U1232201, U1332201.} }

@@

	\begin{abstract}
		ToDo

@@

	\begin{keyword}
		JUNO,  event rate, computing resource
	\end{keyword}

@@

	\footnotetext[0]{\hspace*{-3mm}\raisebox{0.3ex}{$\scriptstyle\copyright$}2013
		Chinese Physical Society and the Institute of High Energy Physics
		of the Chinese Academy of Sciences and the Institute
	of Modern Physics of the Chinese Academy of Sciences and IOP Publishing Ltd}

@@

		The experiment hall is expected to be finished at 2019. 
		It is possible to get data from the experiment at 2020.
		The JUNO event rate is very important for JUNO experiment 
		design. So we want to estimate JUNO
		event rate by theory and Geant4 simulation. The
		JUNO event rate is composed of signal rate and background
		rate.With the estimated JUNO event rate,we can estimate the
		offline computing resource such as cpu, disk, which we 
		needed to do offline data saving and analyzing.The estimated
		JUNO event rate can also help the online electronic design.

>>>>

	%\fancyhead[c]{\small Chinese Physics C~~~Vol. XX, No. X (201X)
	%XXXXXX} \fancyfoot[C]{\small 010201-\thepage}
	%\footnotetext[0]{Received XX XXXX 20XX}

	\title{The event rate estimation for JUNO central detector\thanks{This work is supported by the Strategic Priority Research Program of the Chinese Academy of Sciences, Grant No. XDA10010900; the CAS Center for Excellence in Particle Physics (CCEPP); National Natural Science Foundation of China (NSFC); the Chinese Academy of Sciences (CAS) Large-Scale Scientific Facility Program; Joint Large-Scale Scientific Facility Funds of the NSFC and CAS under Contracts Nos. U1332201.} }

@@

	\begin{abstract}
		The Jiangmen Underground Neutrino Observatory (JUNO) is an experiment proposed to determine
		the neutrino mass hierarchy and probe the fundamental properties of neutrino oscillation. 
		The JUNO central detector is a spherical liquid scintillator detector with 20 kton fiducial mass. 
		The central detector's event rate is very important for JUNO online 
		electronic and DAQ(Data Acquisition)
		system design. It also help us to estimate the offline disk storage sapce for JUNO experiment data.
		So we estimate the event rate of JUNO central detector by threory and Geant4 simulation. 
		We consider many event source such
		as IBD(inverse $\beta$-decay) events, cosmic muon events, the radioactity events from materials of
		central detector, the radioactity events from water pool and rock, the PMT's dark noise events.
		We also propose and do a simulation of a promising secondary trigger system which is intend to
		suppress low energy 
		radioactity background and dark noise. The estimated disk storage sapce for JUNO experiment data
		also be gived.

@@

	\begin{keyword}
		JUNO, event rate, disk storage space
	\end{keyword}

@@

	%\footnotetext[0]{\hspace*{-3mm}\raisebox{0.3ex}{$\scriptstyle\copyright$}2013
	%	Chinese Physical Society and the Institute of High Energy Physics
	%	of the Chinese Academy of Sciences and the Institute
	%of Modern Physics of the Chinese Academy of Sciences and IOP Publishing Ltd}

@@

		The experiment hall is expected to be finished at 2019. 
		It is possible to get data from the experiment at 2020.
		The JUNO event rate is very important for JUNO experiment 
		design. So we want to estimate JUNO
		event rate by theory and Geant4 simulation. The
		JUNO event rate is composed of signal rate and background
		rate.With the estimated JUNO event rate,we can estimate the
		offline disk storage space and help the online electronic and 
		DAQ(Data Acquisition) system design.
